Differential Expression - HBCC - sgACC - Dx

### 2020-05-20 individual-cohorts/HBCC_sgACC_DE.Rmd
fix scaling

```{r iterative.normalisation, results='asis'}
writeLines(glue::glue('Using following covariates in the model:',
                 glue::glue_collapse(adjust.covars, sep = ", ", last = " and "),
                 ' as fixed effects and',
                 glue::glue_collapse(random_effect, sep = ", ", last = " and "),' chosen as random effects'))

col_type <- dplyr::select(COVARIATES, c(adjust.covars, random_effect)) %>%
  dplyr::summarise_all(class) %>% 
  tidyr::gather(variable, class)

# Scale continuous variables
adjust.covars = sapply(1:length(col_type$class), function(i){
  switch(col_type$class[i], 
    "factor" = paste0(col_type$variable[i]),
    "numeric" = paste0('scale(', col_type$variable[i], ')')
  )
  })

# Post adjusted formula
formula <- glue::glue("~ ", glue::glue_collapse(adjust.covars, sep = " + "), " + ", glue::glue_collapse(glue::glue("(1|{random_effect})"), sep = " + "))

>>>>

```{r iterative.normalisation, results='asis'}
writeLines(glue::glue('Using following covariates in the model:',
                 glue::glue_collapse(adjust.covars, sep = ", ", last = " and "),
                 ' as fixed effects and ',
                 glue::glue_collapse(random_effect, sep = ", ", last = " and "),' chosen as random effects'))

scaled_col_type <- dplyr::select(COVARIATES, c(adjust.covars)) %>%
  dplyr::summarise_all(class) %>% 
  tidyr::gather(variable, class)

# Scale continuous variables
scaled_adjust_covars = sapply(1:length(scaled_col_type$class), function(i){
  switch(scaled_col_type$class[i], 
    "factor" = paste0(scaled_col_type$variable[i]),
    "numeric" = paste0('scale(', scaled_col_type$variable[i], ')')
  )
  })

# Post adjusted formula
formula <- glue::glue("~ ", glue::glue_collapse(scaled_adjust_covars, sep = " + "), " + ", glue::glue_collapse(glue::glue("(1|{random_effect})"), sep = " + "))
